---
title: ' draft manuscript'
author: "Liam Wilson"
date: "2024-09-11"
output:
  pdf_document: default
  html_document: default
bibliography: /Users/liamwilson/Desktop/GradSchool/Semesters/FourthSemF2024/ReproducibilityR/ReproducibilityProjectF2024/ReproducibilityGitProject/REmanuscript/updatedreferences.bib
---

# Draft Manuscript for the LDP Reproducibility Class

## Installing Packages

```{r}
options(repos = c(CRAN = "https://cran.rstudio.com/"))
install.packages("rmarkdown")
install.packages("tinytex")
library(rmarkdown)
library(tinytex)
```

##Download Package Pre Reg to make a Prereg File
```{r}
install.packages("prereg")
library(prereg)
install.packages('tinytex')
tinytex::install_tinytex(force=TRUE)
library(tinytex)
```

#Hypotheses and Analysis 
##First Hypothesis
###H0: Plant leaf area will be the same for all elevations 
### H1: Plant leaf area will be larger at lower elevations as a result of increased water and humidity at lower elevations, thus allowing higher growth rates. 

###Install/Load Packages 
```{r}
install.packages("tidyverse")
library(tidyverse)
```

### Anova: Plant leaf area by elevation 

```{r}
leafarea <- hbr_maples %>%
  select(elevation, leaf1area) %>%
  drop_na()

leafareamod <- aov(leaf1area ~ elevation, data =hbr_maples)

summary(leafareamod)

```

###P Value >0.05. Therefore, cannot reject null hypothesis. Leaf area is the same at both low and medium elevations. 

##Second Hypothesis
###H0: Plant stem length will be the same for all elevations 
### H1: Plant stems will be longer at lower elevations as a result of increased water and humidity at lower elevations, thus allowing higher growth rates.

```{r}
stemlength <- hbr_maples %>%
  select(elevation, stem_length) %>%
  drop_na()

stemlengthmod <- aov(stem_length ~ elevation, data =hbr_maples)

summary(stemlengthmod)

```
###P Value >0.05. Therefore, cannot reject null hypothesis. Stem length is the same at both low and medium elevations.

##Third Hypothesis
###H0: Plant dry leaf mass will be the same for all elevations 
### H1: Plant leaf dry mass will be higher at lower elevations as a result of increased water and humidity at lower elevations, thus allowing higher growth rates.

```{r}
dryleafmass <- hbr_maples %>%
  select(elevation, leaf_dry_mass) %>%
  drop_na()

dryleafmod <- aov(leaf_dry_mass ~ elevation, data =hbr_maples)

summary(dryleafmod)

```
###P Value < 0.05. Therefore, we can reject null hypothesis. leaf dry mass is different at low and medium elevations.

##Fourth Hypothesis
###H0: Plant dry stem mass will be the same for all elevations 
### H1: Plant stem dry mass will be higher at lower elevations as a result of increased water and humidity at lower elevations, thus allowing higher growth rates.

```{r}
drystemmass <- hbr_maples %>%
  select(elevation, stem_dry_mass) %>%
  drop_na()

drystemmod <- aov(stem_dry_mass ~ elevation, data =hbr_maples)

summary(drystemmod)

```
###P Value < 0.05. Therefore, we can reject null hypothesis. stem dry mass is different at low and medium elevations.


## Zotero References from .bib file

First citation [@co2elev]

Second citation [@ma2010a]

Third Citation [@zhu2022a]


