---
title: ' draft manuscript'
author: "Liam Wilson"
date: "2024-09-11"
output:/Users/liamwilson/Desktop/GradSchool/Semesters/FourthSemF2024/ReproducibilityR/ReproducibilityProjectF2024/ReproducibilityGitProject/REoutdata
  html_document: default
  pdf_document: default
bibliography: /Users/liamwilson/Desktop/GradSchool/Semesters/FourthSemF2024/ReproducibilityR/ReproducibilityProjectF2024/ReproducibilityGitProject/REmanuscript/updatedreferences.bib
csl: https://www.zotero.org/styles/apa
---

# Draft Manuscript for the LDP Reproducibility Class

##Initializating Package Managment 
```{r}
install.packages("renv")
library(renv)
renv::init()

#For updating any loaded packages use renv::update
```

## Installing Packages

```{r}
options(repos = c(CRAN = "https://cran.rstudio.com/"))
install.packages("rmarkdown")
install.packages("tinytex")
library(rmarkdown)
library(tinytex)
install.packages("tidyverse")
library(tidyverse)
```

## Download Package Pre Reg to make a Prereg File
```{r}
install.packages("prereg")
library(prereg)
install.packages('tinytex')
tinytex::install_tinytex(force=TRUE)
library(tinytex)
```

## Getting Data - Within the Rmd File

```{r}
install.packages("lterdatasampler")
library(lterdatasampler)
hbr_maples <- hbr_maples
view(hbr_maples)
```

##Getting Data - Pulling from RErawdata
```{r}
library(readr)
hbr_maples <- read_csv("ReproducibilityProject2024Archive/00_RErawdata/hbr_maples.csv")
View(hbr_maples)
```


##Note - Alternate way to acess datset is in datascript.R file within the REscripts folder then import dataset from files. 

# Hypotheses and Analysis using One-Way ANOVA's

## First Hypothesis

### H0: Plant leaf area will be the same for all elevations 

### H1: Plant leaf area will be larger at lower elevations as a result of increased water and humidity at lower elevations, thus allowing higher growth rates. 


```{r}
leafarea <- hbr_maples %>%
  select(elevation, leaf1area) %>%
  drop_na()

leafareamod <- aov(leaf1area ~ elevation, data =hbr_maples)

summary(leafareamod)

```

### P Value >0.05. Therefore, cannot reject null hypothesis. Leaf area is the same at both low and medium elevations. 

## Second Hypothesis

### H0: Plant stem length will be the same for all elevations 

### H1: Plant stems will be longer at lower elevations as a result of increased water and humidity at lower elevations, thus allowing higher growth rates.

```{r}
stemlength <- hbr_maples %>%
  select(elevation, stem_length) %>%
  drop_na()

stemlengthmod <- aov(stem_length ~ elevation, data =hbr_maples)

summary(stemlengthmod)

```

### P Value >0.05. Therefore, cannot reject null hypothesis. Stem length is the same at both low and medium elevations.

## Third Hypothesis

### H0: Plant dry leaf mass will be the same for all elevations 

### H1: Plant leaf dry mass will be higher at lower elevations as a result of increased water and humidity at lower elevations, thus allowing higher growth rates.

```{r}
dryleafmass <- hbr_maples %>%
  select(elevation, leaf_dry_mass) %>%
  drop_na()

dryleafmod <- aov(leaf_dry_mass ~ elevation, data =hbr_maples)

summary(dryleafmod)

```

### P Value < 0.05. Therefore, we can reject null hypothesis. leaf dry mass is different at low and medium elevations.

## Fourth Hypothesis
### H0: Plant dry stem mass will be the same for all elevations 

### H1: Plant stem dry mass will be higher at lower elevations as a result of increased water and humidity at lower elevations, thus allowing higher growth rates.

```{r}
drystemmass <- hbr_maples %>%
  select(elevation, stem_dry_mass) %>%
  drop_na()

drystemmod <- aov(stem_dry_mass ~ elevation, data =hbr_maples)

summary(drystemmod)

```

### P Value < 0.05. Therefore, we can reject null hypothesis. stem dry mass is different at low and medium elevations.


## Zotero References from .bib file

First citation [@co2elev]

Second citation [@ma2010a]

Third Citation [@zhu2022a]


